Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers

### 2020-04-06 3d1d_coupled_LM.tex
MK sweep
Arxiv-ed version

\newcommand{\kent}[1]{{\color{blue}#1}}
\newcommand{\miro}[1]{{\color{cyan}#1}}
\newcommand{\paolo}[1]{{\color{magenta}#1}}
% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}

% Authors: full names plus addresses.
\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}

@@

% REQUIRED
\begin{abstract}
Manuscript in preparation, to be kept confidential.
\end{abstract}

% REQUIRED
\begin{keywords}
elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
\end{keywords}

@@

In this study we consider coupled partial differential equations on domains with mixed dimensionality, in particular we address the  3D-1D case. The mathematical structure of such problems can be represented by the following formal equations:
\begin{subequations}
\label{eq:pde}
\begin{align}
\label{eq:pde1}
  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
\label{eq:pde2}
 d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
\label{eq:coupling}
\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
\end{align}
\end{subequations}
Problem \eqref{eq:pde} can be described as an example of \emph{mixed dimensional PDEs}.
Here, $u$, $\ud$,  $\lambda$ are unknowns,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure
parameterized in terms of $s$ and $d_s$ is the derivative with respect to $s$. 
The term $\lambda\delta_{\Lambda}$ is a Dirac measure such that 
$\int_{\Omega}\lambda(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}\lambda(t)v(t) \,\mathrm{d}t$
for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a suitable restriction operator from 3D to 1D.

@@

@@

Let the domain $\Omega\subset \R^3 $ be convex and composed of two parts, 
$\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
Let 
$\Omega_{\ominus}$ be a \emph{generalized cylinder}, c.f.  \cite{MR1940257}, 
that is; the swept volume of a two dimensional set, $\partial\mathcal{D}$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
In detail, the curve 
$\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$,  where 
$\boldsymbol \lambda(s) = [\xi(s), \tau(s), \zeta(s)], \ s\in(0,S)$ is a $\mathcal{C}^2$-regular curve in the three-dimensional domain $\Omega$.
For simplicity, let us assume that $\|\boldsymbol \lambda^\prime(s)\|=1$ such that the arc-length and the coordinate $s$ coincide.
Further, let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section
and $\Gamma$ be the lateral surface of $\Omega_{\ominus}$, i.e.
$\Gamma=\{ \ \partial \mathcal{D}(s) \  | \ s \in \Gamma\}$,
while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
We assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side.
According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
functions defined on $\Omega,\,\Omega_{\oplus},\,\Omega_{\ominus},\,\Lambda$, respectively.

@@

Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
The space of functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
$H^{\frac 1 2}_{00}(\Sigma)$ and we remark that 
$H^{\frac 1 2}_{00}(\Sigma) = \mathcal{T}_\Sigma H^1_0(D)$
and  $H^{-\frac 1 2}(\Sigma) = (H^{\frac 1 2}_{00}(\Sigma))^*$

@@

\kent{
We will frequently use inner products and norms that are weighted. The
$L_2$ and $H^1$ inner products
weighted by a scalar function 
$w$, which is positive almost everywhere,
are defined as 
follows
\begin{eqnarray*}
%(u,v)_{\Gamma, w} = 
(u,v)_{L^2(\Omega), w} &=& 
\int_{\Omega} w \, u \, v d\omega \\
%(u,v)_{\Gamma, w} = 
(u,v)_{H^1(\Omega), w} &=& 
\int_{\Omega}  w \, u \, v d\omega
+ \int_{\Omega} w \, \nabla u \cdot \nabla v d\omega
\end{eqnarray*}
whereas a weighted fractional
space \miro{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
That is, let $S$ denote the
Riesz map such that 
for $u, v \in H^1(\Gamma)$ we have 
\[
(S u,v)_{H^1(\Gamma),w} = (u,v)_{L^2(\Gamma), w}.
\]
Then $S$ is a compact self-adjoint operator. 
Assuming that $\{\lambda_k\}_k$ is the set of eigenvalues, 
$\{\phi_k\}_k$ the set of eigenvectors orthonormal with respect to the inner 
product $(\cdot, \cdot)_{L^2(\Gamma), w}$ and $u\in H^1(\Gamma)$ can be expressed 
as $u=\sum_k c_k \phi_k$ 
then
\[
\|u\|^2_{H^s(\Gamma), w} = \sum \lambda_k^{-1} c_k^2 .   
\]
The space $H_{00}^s(\Gamma; w)$ is defined analogously, but with $S$ above defined in terms of the $H^1_0$ inner product. 
The weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different. \miro{Not sure about the last sentence.}
 }
 Finally, $|\cdot|$ denote the Lebesgue measure of a set, i.e. $|\mathcal{D}(0)|$ is the cross-sectional area of the bottom of the cylinder. In the following we assume that the cross-sectional area $\mathcal{D}(s)$ is constant, namely $\mathcal{D}(s)=\mathcal{D}$, but remark that this assumption is only made to simplify the notation. Central in our analysis are the transverse averages $\avrc{w},\,\avrd{w}$ defined as, 
\begin{gather*}
\avrc{w}(s) = |\partial\mathcal{D}(s)|^{-1} \int_{\partial\mathcal{D}(s)} w d\gamma \quad \mbox{and} \quad 
\avrd{w}(s) = |\mathcal{D}(s)|^{-1} \int_{\mathcal{D}(s)} w d\sigma, 
\end{gather*}
where $d\omega, \ d\sigma, \ d\gamma$ are the generic volume, surface and curvilinear Lebesgue measures.
Clearly, 
\begin{gather*}
\int_{\Omega_{\ominus}} w d\omega 
= \int_\Lambda \int_{\mathcal{D}(s)} w d\sigma ds
= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\, 
\\
\int_{\partial\Omega_{\ominus}} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}(s)} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}(s)| \avrc{w}(s) ds\,. 
\end{gather*}
Analogously, for functions defined on $\Lambda$ and $\Omega_\ominus$ respectively, 
we let  $d_s$ and $\partial_s$ be the ordinary and partial derivative with respect to the arclength.

@@

With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde} and \eqref{inteq:pde}. The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads:  Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
(u,v)_{H^1(\Omega)} 
+  \langle \mtrace v, \ld \rangle_{\Lambda, |\DD|} &= 
(f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,\\
(\ud,\vd)_{H^1(\Lambda),|\D|} - \langle  \vd, \ld \rangle_{\Lambda, |\DD|} 
&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
&\forall \vd \in H^1_0(\Lambda)\, ,\\
\langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} &= 0
&\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
\end{align}
\end{subequations}

In addition to the 3D-1D-1D problem we will also consider an 
intermediate problem where the 3D and 1D problems are coupled at an
intermediate 2D surface  encapsulating the 1D structure. The strong form is \miro{The strong form does not seem correct}:  
\begin{subequations}
\label{inteq:pde}
\begin{align}
\label{inteq:pde1}
  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\ 
\label{inteq:pde2}
 d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
\label{inteq:coupling}
\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Gamma . 
\end{align}
\end{subequations}
The corresponding weak formulation of \eqref{inteq:pde}, referred to as the \textbf{Problem 3D-1D-2D}, reads: 
Find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
\begin{subequations}\label{eq:problem1}
\begin{align}
(u,v)_{H^1(\Omega)} + \langle \trace v, \lambda \rangle_\Gamma &= (f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,
\\
 (\ud,\vd)_{H^1(\Lambda),|\D|}  -  \langle \ext \vd, \lambda \rangle_\Gamma
&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|} &\forall\vd \in H^1(\Lambda)\, ,\\
\langle \trace u - \ext \ud , \mu \rangle_\Gamma &= 0 &\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
\end{align}
\end{subequations}

@@

Under the geometric assumptions stated above for $\Omega,\,\Gamma,\,\Lambda$, Lemma \ref{lemma:H12norm} implies the following result.
\begin{corollary}\label{corollary:H12norm}
If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$ such that
\begin{equation*}
\|\avrc{u}\|_{H^{\frac 12}_{00}(\Lambda), |\DD|} \leq C_\Gamma \|u\|_{H^{\frac 12}_{00}(\Gamma)}.
\end{equation*}
\kent{Here, $C_\Gamma$ is bounded independently of $\mathcal{D}(s)$.} 
\end{corollary}

@@

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 3D-1D-2D}
We aim to find $u \in H^1_0(\Omega),\ \ud \in H_0^1(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$,
solutions of \eqref{eq:saddle-point}, where
\begin{align*}
a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
\\
b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma,
\\
c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
\\
d(\mu)&=0.
\end{align*}
We prove that the conditions of Theorem \ref{th:bnb} are fulfilled choosing 
$X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$, where $X$  is equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + \|\ud\|^2_{H^1(\Lambda),|\D|}$.

@@

\paolo{
To show the inf-sup condition, we will employ $\mathcal{H}_\Omega$ 
a lifting operator from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$.
Using the results of \cite{sauter1999extension} about extension operators for domains having small geometric details (see also \cite{laurino_m2an} for a direct application to this case) there exists a lifting operator $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1(\Omega)$ and the boundedness/stability of this operator ensures that there exists 
$\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{1/2}_{00}(\Gamma)}$
where $\| \mathcal{H}_\Omega \|$ is a constant independent the (minimal) radius of $\Gamma$.
}

@@

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 3D-1D-1D}
We aim to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$,
solution of \eqref{eq:saddle-point} with
\begin{align*}
a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
\\
b([v, \vd], \md)&=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|},
\\
c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
\\
d(\md)&=0.
\end{align*}

@@

The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
\begin{eqnarray}\label{eq:saddle-point_discrete}
\begin{aligned}
a(u_h,v_h)+b(v_h,\lambda_h)&=c(v_h) &&\forall v_h\in X_h,\\
b(u_h,\mu_h)&=d(\mu_h) &&\forall \mu_h\in Q_h,
\end{aligned}
\end{eqnarray}
where with little abuse of notation we use $h$ as the sub-index for all the discretization spaces.
This discrete problem is well-posed if the \eqref{BNB1}-\eqref{BNB4} conditions applies to $X_h$ and $Q_h$. Since $X_h\subset X$ and $Q_h\subset Q$,  
\eqref{BNB1}-\eqref{BNB3} follow immediately and only the inf-sup condition needs consideration.  We summarize this proposition in the Corollary below. 
\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}\\
Let
$X_h \subset X$, $Q_h \subset Q$, $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ satisfy the conditions  \eqref{BNB1}-\eqref{BNB3} then  
the problem \eqref{eq:saddle-point_discrete} is well-posed if 
the discrete counterpart of \eqref{BNB4} is satisfied, i.e.
there exists a constant $\beta_h>0$ such that
\begin{align}
\label{eq:infsup_discrete}
 \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\, .
\end{align}
\end{corollary}

@@

the following upper bound holds true,

>>>>

\newcommand{\kent}[1]{{\color{black}#1}}
\newcommand{\miro}[1]{{\color{black}#1}}
\newcommand{\paolo}[1]{{\color{black}#1}}
% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
% \title{Coupling PDEs on 3D-1D domains\\ with Lagrange multipliers}
\title{Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers}

% Authors: full names plus addresses.
\author{M. Kuchta\thanks{Simula Research Laboratory, Oslo, Norway (\email{miroslav@simula.no})}\and F. Laurino\thanks{MOX, Department of Mathematics, Politecnico di Milano, Italy (\email{federica.laurino@polimi.it})} \and K.A. Mardal\footnotemark[1]$^{\;,}$\thanks{University of Oslo, Department of Mathematics (\email{kent-and@math.uio.no})} \and P. Zunino\thanks{MOX, Department of Mathematics, Politecnico di Milano, Italy (\email{paolo.zunino@polimi.it}), Corresponding Author}}

@@

% REQUIRED
\begin{abstract}
Coupled partial differential equations defined on domains with different dimensionality are usually called mixed dimensional PDEs. We address mixed dimensional PDEs on three-dimensional (3D) and one-dimensional domains, giving rise to a 3D-1D coupled problem.
Such problem poses several challenges from the standpoint of existence of solutions and numerical approximation. For the coupling conditions across dimensions, we consider the combination of essential and natural conditions, basically the combination of Dirichlet and Neumann conditions. To ensure a meaningful formulation of such conditions, we use the Lagrange multiplier method, suitably adapted to the mixed dimensional case. The well posedness of the resulting saddle point problem is analyzed. Then, we address the numerical approximation of the problem in the framework of the finite element method. The discretization of the Lagrange multiplier space is the main challenge. Several options are proposed, analyzed and compared, with the purpose to determine a good balance between the mathematical properties of the discrete problem and flexibility of implementation of the numerical scheme. The results are supported by evidence based on numerical experiments.
\end{abstract}

% REQUIRED
\begin{keywords}
mixed dimensional PDEs, finite elemet approximation, essential coupling conditions, Lagrange multipliers
\end{keywords}

@@

In this study we consider coupled partial differential equations on domains with mixed dimensionality, in particular we address the  3D-1D case. The mathematical structure of such problems can be represented by the following formal equations:
\begin{subequations}
\label{eq:pde}
\begin{align}
\label{eq:pde1}
  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
\label{eq:pde2}
 d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
\label{eq:coupling}
\mathcal{T}_\Lambda u - \ud  &=  \paolo{q} &\mbox{ on } \Lambda . 
\end{align}
\end{subequations}
Problem \eqref{eq:pde} can be described as an example of \emph{mixed dimensional PDEs}.
Here, $u$, $\ud$,  $\lambda$ are unknowns,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure
parameterized in terms of $s$ and $d_s$ is the derivative with respect to $s$. 
The term $\lambda\delta_{\Lambda}$ is a Dirac measure such that 
$\int_{\Omega}\lambda(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}\lambda(t)v(t) \,\mathrm{d}t$
for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a suitable restriction operator from 3D to 1D.

@@

\paolo{Although the focus of the present work is mostly about analysis and approximation of the proposed approach, we stress that it aims to build the mathematical foundations to tackle various applications involving 3D-1D mixed dimensional PDEs, such as FSI of slender bodies \cite{Mori2019887}, microcirculation and lymphatics \cite{Possenti2019101,Vinje2019}, subsurface flow models with wells \cite{Cerroni2019} and the electrical activity of neurons.}

@@

Let the domain $\Omega\subset \R^3 $ be convex and composed of two parts, 
$\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
Let 
$\Omega_{\ominus}$ be a \emph{generalized cylinder}, c.f.  \cite{MR1940257}, 
that is; the swept volume of a two dimensional set, $\partial\mathcal{D}$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
In detail, the curve 
$\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$,  where 
$\boldsymbol \lambda(s) = [\xi(s), \tau(s), \zeta(s)], \ s\in(0,S)$ is a $\mathcal{C}^2$-regular curve in the three-dimensional domain $\Omega$.
For simplicity, let us assume that $\|\boldsymbol \lambda^\prime(s)\|=1$ such that the arc-length and the coordinate $s$ coincide.
Further, let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section
and $\Gamma$ be the lateral surface of $\Omega_{\ominus}$, i.e.
$\Gamma=\{ \ \partial \mathcal{D}(s) \  | \ s \in \Gamma\}$,
while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
We assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side.
 \paolo{Finally, $|\cdot|$ denotes the Lebesgue measure of a set, e.g. $|\mathcal{D}(s)|$ is the cross-sectional area of the cylinder. In general, $|\D(s)|$ must be strictly positive and bounded.}
According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
functions defined on $\Omega,\,\Omega_{\oplus},\,\Omega_{\ominus},\,\Lambda$, respectively.

@@

Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from \kent{$D$} to $\Sigma$.
The space of functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
$H^{\frac 1 2}_{00}(\Sigma)$ and we remark that 
$H^{\frac 1 2}_{00}(\Sigma) = \mathcal{T}_\Sigma H^1_0(D)$
and  $H^{-\frac 1 2}(\Sigma) = (H^{\frac 1 2}_{00}(\Sigma))^*$

@@

\kent{
We will frequently use inner products and norms that are weighted. The
$L_2$ and $H^1$ inner products
weighted by a scalar function 
$w$, which is strictly positive and bounded almost everywhere,
are defined as 
follows
\begin{equation*}
%(u,v)_{\Gamma, w} = 
(u,v)_{L^2(\Omega), w} = 
\int_{\Omega} w \, u \, v d\omega \ \mbox{   and   } \
%(u,v)_{\Gamma, w} = 
(u,v)_{H^1(\Omega), w} = 
\int_{\Omega}  w \, u \, v d\omega
+ \int_{\Omega} w \, \nabla u \cdot \nabla v d\omega
\end{equation*}
whereas a weighted fractional
space \miro{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
For the norm of such spaces, we introduce 
the Riesz map $S$ such that 
for $u, v \in H^1(\Gamma)$ we have 
\[
(S u,v)_{H^1(\Gamma),w} = (u,v)_{L^2(\Gamma), w}.
\]
Then $S$ is a compact self-adjoint operator. 
Assuming that $\{\lambda_k\}_k$ is the set of eigenvalues, 
$\{\phi_k\}_k$ the set of eigenvectors of $S$ 
orthonormal with respect to the inner 
product $(\cdot, \cdot)_{L^2(\Gamma), w}$ and $u\in H^1(\Gamma)$ can be expressed 
as $u=\sum_k c_k \phi_k$ 
then
\[
\|u\|^2_{H^s(\Gamma), w} = \sum_k \lambda_k^{-s} c_k^2 .   
\]
The space $H_{00}^s(\Gamma; w)$ is defined analogously, but with $S$ above defined in terms of the $H^1_0$ inner product. Owing to the positivity and boundedness of $w$ the weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different.
 }

Central in our analysis are the transverse averages $\avrc{w},\,\avrd{w}$ defined as, 
\begin{gather*}
\avrc{w}(s) = |\partial\mathcal{D}(s)|^{-1} \int_{\partial\mathcal{D}(s)} w d\gamma \quad \mbox{and} \quad 
\avrd{w}(s) = |\mathcal{D}(s)|^{-1} \int_{\mathcal{D}(s)} w d\sigma, 
\end{gather*}
where $d\omega, \ d\sigma, \ d\gamma$ are the generic volume, surface and curvilinear Lebesgue measures.
Clearly, 
\begin{gather*}
\int_{\Omega_{\ominus}} w d\omega 
= \int_\Lambda \int_{\mathcal{D}(s)} w d\sigma ds
= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\, 
\\
\int_{\partial\Omega_{\ominus}} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}(s)} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}(s)| \avrc{w}(s) ds\,. 
\end{gather*}
Analogously, for functions defined on $\Lambda$ and $\Omega_\ominus$ respectively, 
we let  $d_s$ and $\partial_s$ be the ordinary and partial derivative with respect to the arclength.

@@

\kent{With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D}. The problem} reads:
\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
\label{eq:problem2a}
(u,v)_{H^1(\Omega)} 
+  \langle \mtrace v, \ld \rangle_{\Lambda, |\DD|} &= 
(f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,
\\
\label{eq:problem2b}
(\ud,\vd)_{H^1(\Lambda),|\D|} - \langle  \vd, \ld \rangle_{\Lambda, |\DD|} 
&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
&\forall \vd \in H^1_0(\Lambda)\, ,
\\
\label{eq:problem2c}
\langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} 
&= \paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}
&\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
\end{align}
\end{subequations}

In addition to the 3D-1D-1D problem we will also consider an 
intermediate problem where the 3D and 1D problems are coupled at an
intermediate 2D surface  encapsulating the 1D structure. The strong form is:  
\paolo{
\begin{subequations}
\label{inteq:pde}
\begin{align}
\label{inteq:pde1}
  -\Delta u + u + \lambda \delta_{\Gamma} &= f &\mbox{ in } \Omega,\\ 
\label{inteq:pde2}
 d_s^2 \ud + \ud -  \avrc{\lambda} &= \avrd{g} &\mbox{ on } \Lambda,\\
\label{inteq:coupling}
\mathcal{T}_\Gamma u - \mathcal{E}_\Gamma \ud  &=  q &\mbox{ on } \Gamma . 
\end{align}
\end{subequations}
}
The corresponding weak formulation of \eqref{inteq:pde}, referred to as the \textbf{Problem 3D-1D-2D}, reads: 
\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
\begin{subequations}\label{eq:problem1}
\begin{align}
(u,v)_{H^1(\Omega)} + \langle \trace v, \lambda \rangle_\Gamma &= (f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,
\\
 (\ud,\vd)_{H^1(\Lambda),|\D|}  -  \langle \ext \vd, \lambda \rangle_\Gamma
&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|} &\forall\vd \in H^1(\Lambda)\, ,
\\
\langle \trace u - \ext \ud , \mu \rangle_\Gamma 
&= \paolo{\langle q,\md\rangle_\Gamma} 
&\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
\end{align}
\end{subequations}

@@

Under the geometric assumptions stated above for $\Omega,\,\Gamma,\,\Lambda$, Lemma \ref{lemma:H12norm} implies the following result.
\begin{corollary}\label{corollary:H12norm}
If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$, \paolo{bounded independently of $\D$ and $\DD$, such that}
\begin{equation*}
\|\avrc{u}\|_{H^{\frac 12}_{00}(\Lambda), |\DD|} \leq C_\Gamma \|u\|_{H^{\frac 12}_{00}(\Gamma)}.
\end{equation*}
\end{corollary}
\paolo{
Furthermore, from the
above Corollary, it is clear that
$\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$.
}

@@

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 3D-1D-2D}
We aim to find $u \in H^1_0(\Omega),\ \ud \in H_0^1(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$,
solutions of \eqref{eq:saddle-point}, where
\begin{align*}
a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
\\
b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma,
\\
c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
\\
d(\mu)&=\paolo{\langle q,\mu\rangle_\Gamma}.
\end{align*}
We prove that the conditions of Theorem \ref{th:bnb} are fulfilled choosing 
$X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$, where $X$  is equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + \|\ud\|^2_{H^1(\Lambda),|\D|}$.

@@

\paolo{
To show the inf-sup condition, we will employ  
a lifting operator,  
$\mathcal{H}_\Omega$,
from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$.
In \cite{sauter1999extension} 
it is established that extension operators for domains having small geometric details (see also \cite{laurino_m2an} for a direct application to this case) there exists a lifting operator $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1(\Omega)$. Further, for this operator   there exists 
$\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{1/2}_{00}(\Gamma)}$
where $\| \mathcal{H}_\Omega \|$ is a constant independent the (minimal) radius of $\Gamma$.
}

@@

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 3D-1D-1D}
We aim to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$,
solution of \eqref{eq:saddle-point} with
\begin{align*}
a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
\\
b([v, \vd], \md)&=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|},
\\
c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
\\
d(\md)&=\paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}.
\end{align*}

@@

The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
\begin{eqnarray}\label{eq:saddle-point_discrete}
\begin{aligned}
a(u_h,v_h)+b(v_h,\lambda_h)&=c(v_h) &&\forall v_h\in X_h,\\
b(u_h,\mu_h)&=d(\mu_h) &&\forall \mu_h\in Q_h,
\end{aligned}
\end{eqnarray}
where with little abuse of notation we use $h$ as the sub-index for all the discretization spaces.
This discrete problem is well-posed if the \eqref{BNB1}-\eqref{BNB4} conditions applies to $X_h$ and $Q_h$. Since $X_h\subset X$ and $Q_h\subset Q$,  
\eqref{BNB1}-\eqref{BNB3} follow immediately and only the inf-sup condition needs consideration.  We summarize this proposition in the Corollary below. 
\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}\\
Let
$X_h \subset X$, $Q_h \subset Q$, $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ satisfy the conditions  \eqref{BNB1}-\eqref{BNB3} then  
the problem \eqref{eq:saddle-point_discrete} is well-posed if 
the discrete counterpart of \eqref{BNB4} is satisfied, i.e.
there exists a constant $\beta_h>0$ such that
\begin{align}
\label{eq:infsup_discrete}
 \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\,, \kent{\quad \forall \mu_h \in Q_h.}
\end{align}
\end{corollary}

@@

the following upper bound holds true
